%-------------------------
% Resume in Latex
% Author : Ethan Hawkins
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ethan Hawkins}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Melbourne}{Melbourne, VIC}
      {BSc, Computing and Software Systems}{Feb. 2022 -- Dec 2024}
      \resumeItem{\textbf{Courses}{: Algorithms and Data Structures, Object Oriented Software Development, Database Systems, Computer Systems, Software Modelling and Design, Quantum Computing, Machine Learning, Linear Algebra, Declarative Programming.}}
  \resumeSubHeadingListEnd


%-----------Extracurriculars-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Altis Consulting - Snowflake, SQL, Python}{Jul. 2023 -- Present}
      {Technology Intern}{Jul 2023 - Oct 2024}
      \resumeItemListStart
        \resumeItem{Developed and integrated 5+ ETL Pipelines for a top client}
        \resumeItem{Streamlined the DevOps process with Python tools to automate compliance checking for code standards, saving 2+ hours of time per deployment cycle.}
        \resumeItem{Engineered complex JavaScript stored procedures in Snowflake to ensure consistency of code across environments, with 100\% code coverage.}
      \resumeItemListEnd
    {\textit{\small{Consultant\hfill Oct. 2024 - Present}}}
    \vspace{-7pt}
    \resumeItemListStart
        \resumeItem{Skipped Graduate role due to high level of responsibility managing the integration of 3+ complex, real-time SQL based systems in an ASX top 20 company.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Experience-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sprout Momentum Master App | TypeScript, Redis, Auth0, AWS}{July 2024 -- Nov 2024}
      {SCRUM Master and Full-Stack Developer}{}
      \resumeItemListStart
        \resumeItem{Developing a productivity app to help professionals take control of their growth through self-reflection.}
        \resumeItem{Driving team collaboration in a group of 5 using SCRUM methodology, executing 3-week sprints, and maintaining detailed documentation on Confluence.}
        \resumeItem{Implementing and managing CI/CD pipelines via Vercel and Gitlab for efficient deployment and integration.}
        \resumeItem{Developed and implemented comprehensive unit tests for backend APIs using Jest, ensuring 95\% code coverage and validating core features including user authentication, data entry, and retrieval.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Personal Portfolio Website | JavaScript, React, HTML, CSS, ThreeJS, Node.js}{2024}
      {Personal Project}{}
      \resumeItemListStart
        \resumeItem{Developed a full frontend website with interactive 3d features to showcase my work.}
        \resumeItem{Learnt vital JavaScript skills on cutting edge frameworks.}
        \resumeItemListEnd
        
    \resumeSubheading
      {JSON Parser| Haskell, Data Structures, Dynamic Programming}{2024}
      {Personal Project}{}
      \resumeItemListStart
        \resumeItem{Wrote a JSON parser using vital computer science concepts in Haskell.}
        \resumeItem{Tested my functional programming skills and strengthened my use of recursion.}
        \resumeItem{Non-Trivial use of data structures and algorithms, using trees, stacks, and grammars.}
        \resumeItemListEnd

        \resumeSubheading
      {IMAP Mail Client| Rust, TCP, UDP, IPs}{2024}
      {University Project}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented a fully featured IMAP mail client in Rust using networking libraries.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Extracurricular}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Code Club Australia}{Jan 2023-Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Volunteered time weekly, to teach primary school aged children how to code in Python.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Courses-----------

%-----------Skill and Interests-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Languages}{: C, Java, Python, JavaScript, SQL, TypeScript, Dart, Haskell, Prolog, Rust, C\#.} \\
     \vspace{1mm}
     \textbf{Developer Tools}{: Git, VS Code, PyCharm, IntelliJ, MySQL, Jupyter, AndroidStudio, Flutter, Node.js, Snowflake, NeoVim, Azure DevOps, SQL Management Studio.} \\
     \textbf{Project Management \& Collaboration Tools}{: Slack, Jira, Confluence, Agile Methodology.} \\
     \vspace{1mm}

    }}
 \end{itemize}
 \begin{center}
    
\small +61403057867 $|$ 
\href{mailto:ADD EMAIL HERE@x.com}{\underline{ethanwhawkins@gmail.com}} $|$
\href{ADD LINKEDIN PAGE HERE}{\underline{linkedin.com/in/ethan-hawkins-24486a244}} 
$|$
\href{ADD LINKEDIN PAGE HERE}{\underline{https://www.computer-games.xyz/}} 

\end{center}


\end{document}